Parity-odd Neutrino Torque Detection

### 2018-10-25 neu_torque.tex
conclusion

Measured from simulations, $(\alpha_1,\alpha_2,\alpha_3)=(-0.18,0.18,0.02)$ in Eq.(\ref{eq.Ir}) optimizes the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. In this case we need $5\times 10^9$ halos to have a $5\sigma$ detection (see Appendix A). If we improve the reconstruction of $\I_R$, the lower limit of required halos is $2\times 10^8$.

@@

\tcb{\textit{Conclusion.---}}

@@

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
\appendix
\section{Errors in 3D}
There are $N$ halos with their unit spin vector randomly distributed on a 2D sphere, $|\spin|=1$ and $\left\langle \spin \right\rangle =\bs{0}$. Adding an additional vector $a\hat{\bs{x}}$ ($a\ll 1$) to $\spin$ and normalize we have $\spin'=(\spin+a\hat{\bs{x}})/|\spin+a\hat{\bs{x}}|$, then we project $\spin'$ onto $\hat{\bs{x}}$ and we get the signal $b=\spin'\cdot\hat{\bs{x}}$. The numerical statistics are as following: $\left\langle b \right\rangle=2a/3$ and $\sigma(b)=1/\sqrt{3N}$. So, to get a $n\sigma$ detection, 
\begin{equation}
	N=3n^2/4a^2 
\end{equation}
halos will be needed.

@@

>>>>

Measured from simulations, $(\alpha_1,\alpha_2,\alpha_3)=(-0.18,0.18,0.02)$ in Eq.(\ref{eq.Ir}) optimizes the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. We then need $5\times 10^9$ halos to have a $5\sigma$ detection (see Appendix \ref{app.error}). If we improve the reconstruction of $\I_R$, the lower limit of required halos is $2\times 10^8$.

@@

\tcb{\textit{Conclusion.---}} 
Enormous efforts has been contributed to the neutrino mass properties.
Radio astronomic and cosmological surveys are promising low-cost experiments implemented in the Universe to probe basic physic mysteries. 
The angular momentum is a 3-dimensional, gravity-driven, parity-odd measure, 
and is easily observable, well modeled by the tidal torque theory, and well conserved over the cosmic evolution.
It contains comparable amount of information as density field but poorly appreciated in application.
The recently developed reconstruction techniques enable us to visit an-order-of-magnitude more precise initial conditions of the Universe in Lagrangian space.

@@

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
\appendix
\section{Errors in 3D}\label{app.error}
There are $N$ halos with their unit spin vector randomly distributed on a 2D sphere, $|\spin|=1$ and $\left\langle \spin \right\rangle =\bs{0}$. Adding an additional vector $a\hat{\bs{x}}$ ($a\ll 1$) to $\spin$ and normalize we have $\spin'=(\spin+a\hat{\bs{x}})/|\spin+a\hat{\bs{x}}|$, then we project $\spin'$ onto $\hat{\bs{x}}$ and we get the signal $b=\spin'\cdot\hat{\bs{x}}$. The numerical statistics are as following: $\left\langle b \right\rangle=2a/3$ and $\sigma(b)=1/\sqrt{3N}$. So, to get a $n\sigma$ detection, 
\begin{equation}
	N=3n^2/4a^2 
\end{equation}
halos will be needed.

@@

\begin{matrix}{ccc}
  & & \\
  & & \\
  & &
\end{matrix}
